Improving \textsl{Gaia} parallaxes with a data-driven model of the color--magnitude diagram

### 2017-02-16 paperDistance/paper.tex
superficial changes; title

\documentclass[iop]{emulateapj}
\newcommand{\myemail}{landerson@simonsfoundation.org}

\slugcomment{Stars are kinda cool again.}

\shorttitle{Measuring Mo' Betta Distances}
\shortauthors{Anderson et al}

@@

\begin{document}\sloppy\sloppypar\raggedbottom\frenchspacing

\title{Mo' Betta Gaia Distance Measurements, \\
    Using Gaia + APASS photometry}

\author{Lauren Anderson\altaffilmark{1},
        David W. Hogg\altaffilmark{1, 2, 3, 4},
        Boris Leistedt\altaffilmark{2},
        Adrian Price-Whelan\altaffilmark{5}}
\altaffiltext{1}{Center for Computational Astrophysics, Flatiron Institute, Simons Foundation, New York City}
\altaffiltext{2}{Center for Cosmology and Particle Physics, Department of Physics, New York University}
\altaffiltext{3}{Center for Data Science, New York University}
\altaffiltext{4}{Max-Planck-Institut f\"ur Astronomie, Heidelberg}
\altaffiltext{5}{Princeton University Observatory, Princeton University}

@@

With projects like \project{The Cannon} (DWH CITE) and \project{Avast}
(DWH CITE), we are exploring the extent to which our predictive models of
stars could be purely data-driven or statistical.
That is, under what circumstances could the data themselves deliver
more precise or more accurate models than any theoretical or
physics-based model?
The answer to this question is extremely context dependent: It depends
on what data are available, how much data are available, and what
questions are being answered.
In general, data-driven models contain fewer assumptions than
physics-driven models, but they are also usually less interpretable.
However, the \gaia\ use case is ideal for thinking about purely statistical
models of stars:
The nearby stars are measured at very high signal-to-noise and can be
used to anchor empirical models that can be applied to the more
distant stars.

>>>>

\documentclass[12pt, preprint]{aastex6}
\hypersetup{colorlinks = false}

%% Begin DWH mods
\setlength{\voffset}{0in}
\setlength{\hoffset}{0in}
\setlength{\textwidth}{6in}
\setlength{\textheight}{9in}
\setlength{\headheight}{0ex}
\setlength{\footnotesep}{0in}
\setlength{\topmargin}{-\headsep}
\setlength{\oddsidemargin}{0.25in}
\setlength{\evensidemargin}{0.25in}
\linespread{1.09}
\setlength{\parindent}{1.2\baselineskip}
\makeatletter % you know you are living your life wrong when you need to do this
\long\def\frontmatter@title@above{
\vspace*{-\headsep}\vspace*{\headheight}
\noindent\footnotesize
{\noindent\footnotesize\textsc{\@journalinfo}}\par
{\noindent\scriptsize Preprint typeset using \LaTeX\ style AASTeX6
with modifications by DWH.
}\par\vspace*{-\baselineskip}\vspace*{0.625in}
}%
\long\def\frontmatter@abstractheading{%
\makeaffils
  \vspace*{-\baselineskip}\vspace*{1.5pt}
  \vspace*{0.13189in}
 \begingroup
  \centering
  \abstractname
  \vskip 1mm
  \par
 \endgroup
 \everypar{\rightskip=0.0in\leftskip=\rightskip}\par
}%
\def\frontmatter@keys@format{\vspace*{0.5mm}%
  \settowidth{\keys@width}{\normalsize\@keys@name}%
  \rightskip=0.0in\leftskip=\rightskip\parindent=0pt%
    \hangindent=\keys@width\hangafter=1\normalsize\raggedright}%
\def\twodigits#1{\ifnum#1<10 0\fi\the#1}
\def\mydate{\leavevmode\hbox{\the\year-\twodigits\month-\twodigits\day}}
\makeatother
%% End DWH mods

@@

\newcommand{\myemail}{landerson@simonsfoundation.org}
\slugcomment{Draft manuscript not ready for distribution. \textbf{Copyright 2017 the authors.}}
\shorttitle{Improving Gaia parallaxes}
\shortauthors{Anderson, Hogg, Leistedt, Price-Whelan}
\begin{document}\sloppy\sloppypar\raggedbottom\frenchspacing

\title{Improving \textsl{Gaia} parallaxes
       with a data-driven model of the color--magnitude diagram}
\author{Lauren Anderson\altaffilmark{1},
        David W. Hogg\altaffilmark{1,2,3,4},
        Boris Leistedt\altaffilmark{2},
        Adrian Price-Whelan\altaffilmark{5}}
\altaffiltext{1}{Center for Computational Astrophysics, Flatiron Institute, Simons Foundation, New York City}
\altaffiltext{2}{Center for Cosmology and Particle Physics, Department of Physics, New York University}
\altaffiltext{3}{Center for Data Science, New York University}
\altaffiltext{4}{Max-Planck-Institut f\"ur Astronomie, Heidelberg}
\altaffiltext{5}{Princeton University Observatory, Princeton University}

@@

With projects like \project{The Cannon} (DWH CITE) and \project{Avast}
(DWH CITE), we are exploring the extent to which our predictive models of
stars could be purely data-driven or statistical.
That is, under what circumstances could the data themselves deliver
more precise or more accurate information than any theoretical or
physics-based model?
The answer to this question is extremely context-dependent: It depends
on what data are available, how much data are available, and what
questions are being answered.
In general, data-driven models contain fewer assumptions than
physics-driven models, but they are also usually less interpretable.
However, the \gaia\ use case is ideal for thinking about purely statistical
models of stars:
The nearby stars are measured at very high signal-to-noise and can be
used to anchor empirical models that can be applied to the more
distant stars.
